The Astropy Project

### 2017-12-14 author.tex
collect common affiliations to avoid spelling errors

\newcommand{\affilprinceton}{Department of Astrophysical Sciences, Princeton University, Princeton, NJ 08544, USA}
\newcommand{\affilmit}{Massachusetts Institute of Technology, Kavli Institute for Astrophysics and Space Research, 70 Vassar St., Cambridge, MA 02139, USA}
\newcommand{\affilstsci}{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}

@@

\author[0000-0003-0872-7098]{A. M. Price-Whelan}
\affiliation{\affilprinceton}

@@

\author[0000-0003-4243-2840]{H. M. G\"{u}nther}
\affiliation{\affilmit}

\author[0000-0003-0079-4114]{P. L. Lim}
\affiliation{\affilstsci}

\author[0000-0002-8969-5229]{S. M. Crawford}
\affiliation{South African Astronomical Observatory, PO Box 9, Observatory 7935, Cape Town, South Africa}

\author{S. Conseil}
\affiliation{Univ Lyon, Univ Lyon1, Ens de Lyon, CNRS, Centre de Recherche Astrophysique de Lyon UMR5574, F-69230, Saint-Genis- Laval, France}

@@

\author[0000-0001-7988-8919]{M. W. Craig}
\affiliation{Minnesota State University Moorhead/Department of Physics and Astronomy, 1104 7th Ave S, Moorhead, MN 56563}

\author[0000-0002-5686-9632]{N. Dencheva}
\affiliation{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}

@@

\author[0000-0002-7908-9284]{L. D. Bradley}
\affiliation{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}

@@

\author[0000-0002-0455-9384]{M. de Val-Borro}
\affiliation{NASA Goddard Space Flight Center, Astrochemistry Laboratory, 8800 Greenbelt Road, Greenbelt, MD 20771, USA}

@@

\author{T. L. Aldcroft}
\affiliation{Harvard/Smithsonian Center for Astrophysics, 60 Garden St., Cambridge, MA, 02138, USA}

@@

\author[0000-0002-9599-310X]{E. J. Tollerud}
\affiliation{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}

@@

\author{C. Ardelean}
\affiliation{Western University/Physics and Astronomy, 1151 Richmond St, London ON, N6A 3K7, Canada}

@@

\author[0000-0002-3306-3484]{G. Barentsen}
\affiliation{NASA Ames Research Center, Moffett Field, CA 94043, USA}

\author[0000-0003-2767-0090]{P. Barmby}
\affiliation{University of Western Ontario/Department of Physics \& Astronomy, 1151 Richmond St, London ON N5X4H1 Canada}

@@

\author{F. Biscani}
\affiliation{Max Planck Institute for Astronomy}

@@

\author{K. A. Bostroem}
\affiliation{UC Davis/Department of Physics, 1 Shields Ave, Davis, CA, 95616, USA}

\author{L. G. Bouma}
\affiliation{Department of Astrophysical Sciences, Princeton University, Princeton, NJ 08540, USA}

\author[0000-0003-2680-005X]{G. B. Brammer}
\affiliation{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}

@@

\author{H. Breytenbach}
\affiliation{South African Astronomical Observatory, PO Box 9, Observatory 7935, Cape Town, South Africa}

@@

\author[0000-0003-4428-7835]{D. J. Burke}
\affiliation{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA, 02138, USA}

@@

\author{M. Cara}
\affiliation{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}

\author{J. V. M. Cardoso}
\affiliation{Universidade Federal de Campina Grande, Campina Grande, PB 58429-900, Brazil; NASA Ames Research Center, Mountain View, CA 94035, USA; Bay Area Environmental Research Institute, Petaluma, CA 94952, USA}

\author{S. Cheedella}
\affiliation{Department of Physics, Blacksburg VA, USA}

\author[0000-0002-5317-7518]{Y. Copin}
\affiliation{Université de Lyon, F-69622, Lyon, France; Université de Lyon 1, Villeurbanne; CNRS/IN2P3, Institut de Physique Nucléaire de Lyon}

\author[0000-0003-1204-3035]{D. Crichton}
\affiliation{Department of Physics and Astronomy, Johns Hopkins University, Baltimore, MD 21218, USA}

\author{D. D'Avella}
\affiliation{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}

\author[0000-0002-4198-4005]{C. Deil}
\affiliation{Max-Planck-Institut f\"ur Kernphysik, PO Box 103980, 69029 Heidelberg, Germany}

\author[0000-0003-0526-3873]{\'{E}. Depagne}
\affiliation{South African Astronomical Observatory, PO Box 9, Observatory 7935, Cape Town, South Africa}

\author[0000-0002-8134-9591]{J. P. Dietrich}
\affiliation{Faculty of Physics, Ludwig-Maximilians-Universit\"at, Scheinerstr. 181679 Munich, Germany;Excellence Cluster Universe, Boltzmannstr. 2, 85748 Garching b. M\"unchen, Germany}

\author{A. Donath}
\affiliation{Max-Planck-Institut f\"ur Kernphysik, PO Box 103980, 69029 Heidelberg, Germany}

\author{T. Erben}
\affiliation{Argelander-Institut f\"ur Astronomie, Auf dem H\"ugel 71, 53121 Bonn / Germany}

@@

\author[0000-0002-9853-5673]{L. H. Garrison}
\affiliation{Harvard-Smithsonian Center for Astrophysics, 60 Garden St., Cambridge, MA, 02138, USA}

\author{S. L. J. Gibbons}
\affiliation{Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge, CB3 0HA, UK}

\author{D. A. Goldstein}
\affiliation{Department of Astronomy, UC Berkeley, 501 Campbell Hall \#3411, Berkeley, CA 94720, USA; Berkeley Lab, 1 Cyclotron Road, Berkeley, CA 94720, USA}

@@

\author[0000-0003-4970-2874]{J. P. Greco}
\affiliation{Department of Astrophysical Sciences,  Princeton University, Princeton, NJ 08544, USA}

\author{P. Greenfield}
\affiliation{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}

@@

\author[0000-0003-2031-7737]{A. Hagen}
\affiliation{Vizual.ai, 3600 O'Donnell St, Suite 250, Baltimore, MD 21224 ; Dept of Astronomy and Astrophysics, Pennsylvania State University, University Park, PA 16802}

\author{P. Hirst}
\affiliation{Gemini Observatory, 670 N. Aohoku Pl, Hilo, HI 96720, USA}

@@

\author[0000-0002-0832-2974]{G. Hosseinzadeh}
\affiliation{Las Cumbres Observatory, 6740 Cortona Drive, Suite 102, Goleta, CA 93117-5575, USA; Department of Physics, University of California, Santa Barbara, CA 93106-9530, USA}

@@

\author[0000-0003-4989-0289]{J. S. Hunkeler}
\affiliation{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}

\author[0000-0001-5250-2633]{\v{Z}. Ivezi\'{c}}
\affiliation{Department of Astronomy, University of Washington, Seattle, WA 98155}

@@

\author{G. Kanarek}
\affiliation{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}

\author[0000-0002-7612-0469]{S. Kendrew}
\affiliation{European Space Agency, Space Telescope Science Institute, 3700 San Martin Drive, Baltimore MD 21231, USA}

\author[0000-0002-8211-1892]{N. S. Kern}
\affiliation{UC Berkeley Department of Astronomy, 501 Campbell Hall, Berkeley, CA, 94709}

\author[0000-0002-0479-7235]{W. E. Kerzendorf}
\affiliation{European Southern Observatory, Karl-Schwarzschild-Stra{\ss}e 2, 85748 Garching bei M\"{u}nchen, Germany}

@@

\author{J. King}
\affiliation{Max-Planck-Institut f\"ur Kernphysik, PO Box 103980, 69029 Heidelberg, Germany}

@@

\author[0000-0001-7221-855X]{S. P. Littlefair}
\affiliation{Dept of Physics \& Astronomy, University of Sheffield, Sheffield, S3 7RH, UK}

@@

\author[0000-0002-1395-8694]{D. M. Macleod}
\affiliation{}

@@

\author[0000-0001-5807-7893]{C. McCully}
\affiliation{Las Cumbres Observatory, 6740 Cortona Drive, Suite 102, Goleta, CA 93117-5575, USA; Department of Physics, University of California, Santa Barbara, CA 93106-9530, USA}

@@

\author[0000-0003-2528-3409]{B. M. Morris}
\affiliation{Astronomy Department, University of Washington, Seattle, WA 98195, USA}

\author[0000-0003-4217-4642]{S. J. Mumford}
\affiliation{SP$^{2}$RC, School of Mathematics and Statistics, The University of Sheffield U.K.}

@@

\author[0000-0001-6628-8033]{N. A. Murphy}
\affiliation{Harvard-Smithsonian Center for Astrophysics, 60 Garden St, Cambridge, MA 02138, USA}

\author{S. Nelson}
\affiliation{Minnesota State University Moorhead, 1104 7th Avenue South Moorhead, MN 56563, United States}

@@

\author[0000-0001-8720-5612]{J. P. Ninan}
\affiliation{The Pennsylvania State University, University Park, PA, USA}

@@

\author{S. Ogaz}
\affiliation{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}

\author[0000-0001-7790-5308]{S. Oh}
\affiliation{Department of Astrophysical Sciences, Princeton University, Princeton, NJ 08544, USA}

\author{J. K. Parejko}
\affiliation{Department of Astronomy, University of Washington, Box 351580, Seattle, WA 98195, USA}

@@

\author{L. E. Sherbert}
\affiliation{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}

@@

\author{A. Y. Shih}
\affiliation{NASA Goddard Space Flight Center, 8800 Greenbelt Road, Greenbelt, MD 20771, USA}

@@

\author[0000-0001-9898-5597]{L. P. Singer}
\affiliation{Astroparticle Physics Laboratory, NASA Goddard Space Flight Center, Code 661, 8800 Greenbelt Rd., Greenbelt, MD 20771, USA}

@@

\author{S. W. Thomas}
\affiliation{Institute of Astronomy, University of Cambridge, Cambridge CB3 0HA, UK}

\author{J. E. H. Turner}
\affiliation{Gemini Observatory, Casilla 603, La Serena, Chile}

@@

\author[0000-0002-6219-5558]{A. de la Vega}
\affiliation{Department of Physics and Astronomy, Johns Hopkins University, 3400 N Charles Street, Baltimore, MD 21218}

\author[0000-0002-1343-134X]{L. L. Watkins}
\affiliation{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}

@@

\author[0000-0002-2958-4738]{J. Woillez}
\affiliation{European Southern Observatory - Karl-Schwarzschild-Str. 2, Garching bei München, D-85748, Germany}

>>>>

\newcommand{\afprinceton}{Department of Astrophysical Sciences, Princeton University, Princeton, NJ 08544, USA}
\newcommand{\afstsci}{Space Telescope Science Institute, 3700 San Martin Dr., Baltimore, MD 21218, USA}
\newcommand{\afsaao}{South African Astronomical Observatory, PO Box 9, Observatory 7935, Cape Town, South Africa}
\newcommand{\afminnstate}{Department of Physics and Astronomy, Minnesota State University Moorhead, 1104 7th Ave S, Moorhead, MN 56563}
\newcommand{\afgoddard}{NASA Goddard Space Flight Center, 8800 Greenbelt Road, Greenbelt, MD 20771, USA}
\newcommand{\afcfa}{Harvard-Smithsonian Center for Astrophysics, 60 Garden St., Cambridge, MA, 02138, USA}
\newcommand{\afwesternontario}{Department of Physics \& Astronomy, University of Western Ontario, 1151 Richmond St, London ON N5X4H1 Canada}
\newcommand{\afnasaames}{NASA Ames Research Center, Moffett Field, CA 94043, USA}
\newcommand{\afjhu}{Department of Physics and Astronomy, Johns Hopkins University, Baltimore, MD 21218, USA}
\newcommand{\afmpik}{Max-Planck-Institut f\"ur Kernphysik, PO Box 103980, 69029 Heidelberg, Germany}
\newcommand{\afioa}{Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge, CB3 0HA, UK}
\newcommand{\afpennstate}{Dept of Astronomy and Astrophysics, Pennsylvania State University, University Park, PA 16802}
\newcommand{\afgemini}{Gemini Observatory, 670 N. Aohoku Pl, Hilo, HI 96720, USA}
\newcommand{\aflco}{Las Cumbres Observatory, 6740 Cortona Drive, Suite 102, Goleta, CA 93117-5575, USA}
\newcommand{\afucsb}{Department of Physics, University of California, Santa Barbara, CA 93106-9530, USA}
\newcommand{\afesomunich}{European Southern Observatory, Karl-Schwarzschild-Stra{\ss}e 2, 85748 Garching bei M\"{u}nchen, Germany}
\newcommand{\afuw}{Department of Astronomy, University of Washington, Seattle, WA 98155}
\newcommand{\afberkeleyastro}{Department of Astronomy, UC Berkeley, 501 Campbell Hall \#3411, Berkeley, CA 94720, USA}

@@

\author[0000-0003-0872-7098]{A. M. Price-Whelan}
\affiliation{\afprinceton}

@@

\author[0000-0003-4243-2840]{H. M. G\"{u}nther}
\affiliation{Kavli Institute for Astrophysics and Space Research, Massachusetts Institute of Technology, 70 Vassar St., Cambridge, MA 02139, USA}

\author[0000-0003-0079-4114]{P. L. Lim}
\affiliation{\afstsci}

\author[0000-0002-8969-5229]{S. M. Crawford}
\affiliation{\afsaao}

\author{S. Conseil}
\affiliation{Univ Lyon, Univ Lyon1, Ens de Lyon, CNRS, Centre de Recherche Astrophysique de Lyon UMR5574, F-69230, Saint-Genis-Laval, France}

@@

\author[0000-0001-7988-8919]{M. W. Craig}
\affiliation{\afminnstate}

\author[0000-0002-5686-9632]{N. Dencheva}
\affiliation{\afstsci}

@@

\author[0000-0002-7908-9284]{L. D. Bradley}
\affiliation{\afstsci}

@@

\author[0000-0002-0455-9384]{M. de Val-Borro}
\affiliation{Astrochemistry Laboratory, \afgoddard}

@@

\author{T. L. Aldcroft}
\affiliation{\afcfa}

@@

\author[0000-0002-9599-310X]{E. J. Tollerud}
\affiliation{\afstsci}

@@

\author{C. Ardelean}
\affiliation{\afwesternontario}

@@

\author[0000-0002-3306-3484]{G. Barentsen}
\affiliation{\afnasaames}

\author[0000-0003-2767-0090]{P. Barmby}
\affiliation{\afwesternontario}

@@

\author{F. Biscani}
\affiliation{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69117 Heidelberg, Germany}

@@

\author{K. A. Bostroem}
\affiliation{Department of Physics, UC Davis, 1 Shields Ave, Davis, CA, 95616, USA}

\author{L. G. Bouma}
\affiliation{\afprinceton}

\author[0000-0003-2680-005X]{G. B. Brammer}
\affiliation{\afstsci}

@@

\author{H. Breytenbach}
\affiliation{\afsaao}

@@

\author[0000-0003-4428-7835]{D. J. Burke}
\affiliation{\afcfa}

@@

\author{M. Cara}
\affiliation{\afstsci}

\author{J. V. M. Cardoso}
\affiliation{Universidade Federal de Campina Grande, Campina Grande, PB 58429-900, Brazil}
\affiliation{\afnasaames}
\affiliation{Bay Area Environmental Research Institute, Petaluma, CA 94952, USA}

\author{S. Cheedella}
\affiliation{Department of Physics, Virginia Tech, Blacksburg, VA 24061, USA}

\author[0000-0002-5317-7518]{Y. Copin}
\affiliation{CNRS/IN2P3, Institut de Physique Nucleaire de Lyon, Universite de Lyon, Universite de Lyon 1, Villeurbanne, F-69622, Lyon, France}

\author[0000-0003-1204-3035]{D. Crichton}
\affiliation{\afjhu}

\author{D. D'Avella}
\affiliation{\afstsci}

\author[0000-0002-4198-4005]{C. Deil}
\affiliation{\afmpik}

\author[0000-0003-0526-3873]{\'{E}. Depagne}
\affiliation{\afsaao}

\author[0000-0002-8134-9591]{J. P. Dietrich}
\affiliation{Faculty of Physics, Ludwig-Maximilians-Universit\"at, Scheinerstr. 181679 Munich, Germany}
\affiliation{Excellence Cluster Universe, Boltzmannstr. 2, 85748 Garching b. M\"unchen, Germany}

\author{A. Donath}
\affiliation{\afmpik}

\author{T. Erben}
\affiliation{Argelander-Institut f\"ur Astronomie, Auf dem H\"ugel 71, 53121 Bonn, Germany}

@@

\author[0000-0002-9853-5673]{L. H. Garrison}
\affiliation{\afcfa}

\author{S. L. J. Gibbons}
\affiliation{\afioa}

\author{D. A. Goldstein}
\affiliation{\afberkeleyastro}
\affiliation{Lawrence Berkeley National Laboratory, 1 Cyclotron Road, Berkeley, CA 94720, USA}

@@

\author[0000-0003-4970-2874]{J. P. Greco}
\affiliation{\afprinceton}

\author{P. Greenfield}
\affiliation{\afstsci}

@@

\author[0000-0003-2031-7737]{A. Hagen}
\affiliation{Vizual.ai, 3600 O'Donnell St, Suite 250, Baltimore, MD 21224}
\affiliation{\afpennstate}

\author{P. Hirst}
\affiliation{\afgemini}

@@

\author[0000-0002-0832-2974]{G. Hosseinzadeh}
\affiliation{\aflco}
\affiliation{\afucsb}

@@

\author[0000-0003-4989-0289]{J. S. Hunkeler}
\affiliation{\afstsci}

\author[0000-0001-5250-2633]{\v{Z}. Ivezi\'{c}}
\affiliation{\afuw}

@@

\author{G. Kanarek}
\affiliation{\afstsci}

\author[0000-0002-7612-0469]{S. Kendrew}
\affiliation{European Space Agency, \afstsci}

\author[0000-0002-8211-1892]{N. S. Kern}
\affiliation{\afberkeleyastro}

\author[0000-0002-0479-7235]{W. E. Kerzendorf}
\affiliation{\afesomunich}

@@

\author{J. King}
\affiliation{\afmpik}

@@

\author[0000-0001-7221-855X]{S. P. Littlefair}
\affiliation{Department of Physics \& Astronomy, University of Sheffield, Sheffield, S3 7RH, UK}

@@

\author[0000-0002-1395-8694]{D. M. Macleod}
\affiliation{Cardiff University, Cardiff CF24 3AA, UK}

@@

\author[0000-0001-5807-7893]{C. McCully}
\affiliation{\aflco}
\affiliation{\afucsb}

@@

\author[0000-0003-2528-3409]{B. M. Morris}
\affiliation{\afuw}

\author[0000-0003-4217-4642]{S. J. Mumford}
\affiliation{SP$^{2}$RC, School of Mathematics and Statistics, The University of Sheffield, U.K.}

@@

\author[0000-0001-6628-8033]{N. A. Murphy}
\affiliation{\afcfa}

\author{S. Nelson}
\affiliation{\afminnstate}

@@

\author[0000-0001-8720-5612]{J. P. Ninan}
\affiliation{\afpennstate}

@@

\author{S. Ogaz}
\affiliation{\afstsci}

\author[0000-0001-7790-5308]{S. Oh}
\affiliation{\afprinceton}

\author{J. K. Parejko}
\affiliation{\afuw}

@@

\author{L. E. Sherbert}
\affiliation{\afstsci}

@@

\author{A. Y. Shih}
\affiliation{\afgoddard}

@@

\author[0000-0001-9898-5597]{L. P. Singer}
\affiliation{Astroparticle Physics Laboratory, \afgoddard}

@@

\author{S. W. Thomas}
\affiliation{\afioa}

\author{J. E. H. Turner}
\affiliation{\afgemini}

@@

\author[0000-0002-6219-5558]{A. de la Vega}
\affiliation{\afjhu}

\author[0000-0002-1343-134X]{L. L. Watkins}
\affiliation{\afstsci}

@@

\author[0000-0002-2958-4738]{J. Woillez}
\affiliation{\afesomunich}
